---
title: "Report template for maps"
author: "Rene Cartaya"
date: "15-05-2022"
output: pdf_document
---

# Mapas

Some embedded interesting maps

# Hexagonal Map


```{r mapaBasico, echo=FALSE}

# World map is available in the maps package
library(maps)

# No margin
par(mar=c(0,0,0,0))

# World map
map('world',
    col="#f2f2f2", fill=TRUE, bg="white", lwd=0.05,
    mar=rep(0,4),border=0, ylim=c(-80,80) 
)
```

\clearpage

# Setting map with linked cities

In the chunk bellow we can set cities we want to display on the map and in the following examples we will be addig different features

```{r MapaBasico2, echo=FALSE}

# Dplyr for data wrangling and pipe function
library(dplyr)

# Cities
Caracas <- c(-66,11)
Santiago <- c(-70,-34.3)
Buenos_aires <- c(-58,-34)
Madrid <- c(-5,41)
Paris <- c(2,49)
Bremen <- c(10,53.5)
Melbourne <- c(145,-38)

# Data frame
data <- rbind(Caracas, Santiago, Buenos_aires, Madrid, Paris, Bremen, Melbourne) %>% 
  as.data.frame()
colnames(data) <- c("long","lat")

# Show the cities on the map
map('world',
    col="#f2f2f2", fill=TRUE, bg="white", lwd=0.05,
    mar=rep(0,4),border=0, ylim=c(-80,80) 
)
points(x=data$long, y=data$lat, col="slateblue", cex=1, pch=20)


```

\clearpage

# Map with travel links basic

In this we can add lines that links different cities

```{r MapaBasico3, echo=FALSE}

# Load geosphere
library(geosphere)

# Background map
map('world',
    col="#f2f2f2", fill=TRUE, bg="white", lwd=0.05,
    mar=rep(0,4),border=0, ylim=c(-80,80) 
)

# Dot for cities
points(x=data$long, y=data$lat, col="slateblue", cex=3, pch=20)

# Compute the connection between Buenos Aires and Paris
inter <- gcIntermediate(Paris,  Buenos_aires, n=50, addStartEnd=TRUE, breakAtDateLine=F)

# Show this connection
lines(inter, col="slateblue", lwd=2)

# Between Paris and Melbourne
inter <- gcIntermediate(Melbourne,  Paris, n=50, addStartEnd=TRUE, breakAtDateLine=F)             
lines(inter, col="slateblue", lwd=2)

```

\clearpage

# Map with travel links

```{r otromapita, echo=FALSE}

# A function that keeps the good part of the great circle, by Jeff Leek:
getGreatCircle <- function(userLL,relationLL){
  tmpCircle = greatCircle(userLL,relationLL, n=200)
  start = which.min(abs(tmpCircle[,1] - data.frame(userLL)[1,1]))
  end = which.min(abs(tmpCircle[,1] - relationLL[1]))
  greatC = tmpCircle[start:end,]
  return(greatC)
}

# background map
map('world',col="#f2f2f2", fill=TRUE, bg="white", lwd=0.05,mar=rep(0,4),border=0, ylim=c(-80,80) )

# map 3 connections:
great <- getGreatCircle(Paris, Melbourne)
lines(great, col="skyblue", lwd=2)
great <- getGreatCircle(Buenos_aires, Melbourne)
lines(great, col="skyblue", lwd=2)
great <- getGreatCircle(Paris, Buenos_aires)
lines(great, col="skyblue", lwd=2)

# City names and dots
points(x=data$long, y=data$lat, col="slateblue", cex=3, pch=20)
text(rownames(data), x=data$long, y=data$lat,  col="slateblue", cex=1, pos=4)

```

\clearpage

# World map

```{r mapEU, echo=FALSE}

# Libraries
library(ggplot2)
library(dplyr)
require(maps)
require(viridis)


theme_set(
  theme_void()
  )

world_map <- map_data("world")
ggplot(world_map, aes(x = long, y = lat, group = group)) +
  geom_polygon(fill="lightgray", colour = "white")


```


\clearpage



# Europe Map


```{r mapaEU, echo=FALSE}

# Some EU Contries
some.eu.countries <- c(
  "Portugal", "Spain", "France", "Switzerland", "Germany",
  "Austria", "Belgium", "UK", "Netherlands",
  "Denmark", "Poland", "Italy", 
  "Croatia", "Slovenia", "Hungary", "Slovakia",
  "Czech republic","Serbia","Kosovo","Montenegro",
  "Albania","Greece","Bosnia and Herzegovina",
  "Finland","Norway","Sweden","Iceland",
  "Lithuania","Latvia", "Estonia"
)
# Retrievethe map data
some.eu.maps <- map_data("world", region = some.eu.countries)

# Compute the centroid as the mean longitude and lattitude
# Used as label coordinate for country's names
region.lab.data <- some.eu.maps %>%
  group_by(region) %>%
  summarise(long = mean(long), lat = mean(lat))

ggplot(some.eu.maps, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = region))+
  geom_text(aes(label = region), data = region.lab.data,  size = 4, hjust = 0.5)+
  scale_fill_viridis_d()+
  theme_void()+
  theme(legend.position = "none")

```

\clearpage

# DACH region Map

```{r mapaDACH, echo=FALSE}

# Germany
some.eu.countries <- c(
  "Germany","Austria","Switzerland"
)
# Retrievethe map data
some.eu.maps <- map_data("world", region = some.eu.countries)

# Compute the centroid as the mean longitude and lattitude
# Used as label coordinate for country's names
region.lab.data <- some.eu.maps %>%
  group_by(region) %>%
  summarise(long = mean(long), lat = mean(lat))

ggplot(some.eu.maps, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = region))+
  geom_text(aes(label = region), data = region.lab.data,  size = 4, hjust = 0.5)+
  scale_fill_viridis_d()+
  theme_void()+
  theme(legend.position = "none")

```

# UK Map

```{r mapaUK, echo=FALSE}

# Libraries
library(ggplot2)
library(dplyr)

# Get the world polygon and extract UK
library(maps)
UK <- map_data("world") %>% filter(region=="UK")

# Get a data frame with longitude, latitude, and size of bubbles (a bubble = a city)
data <- world.cities %>% filter(country.etc=="UK")

# Left chart
ggplot() +
  geom_polygon(data = UK, aes(x=long, y = lat, group = group), fill="grey", alpha=0.3) +
  geom_point( data=data, aes(x=long, y=lat)) +
  theme_void() + ylim(50,59) + coord_map() 
```

# UK Map with cities


```{r mapapequeño2, echo=FALSE}

# Second graphic with names of the 10 biggest cities
library(ggrepel)
ggplot() +
  geom_polygon(data = UK, aes(x=long, y = lat, group = group), fill="grey", alpha=0.3) +
  geom_point( data=data, aes(x=long, y=lat, alpha=pop)) +
  geom_text_repel( data=data %>% arrange(pop) %>% tail(10), aes(x=long, y=lat, label=name), size=5) +
  geom_point( data=data %>% arrange(pop) %>% tail(10), aes(x=long, y=lat), color="red", size=3) +
  theme_void() + ylim(50,59) + coord_map() +
  theme(legend.position="none")

```


# Latin American Map

```{r mapaLA, echo=FALSE}

# Some EU Contries
some.la.countries <- c(
  "Venezuela", "Colombia","Guyana","Ecuador", "Peru","Bolivia",
  "Chile","Argentina","Paraguay", "Uruguay","Brazil",
  "Panama","Costa Rica","Nicaragua","Salvador","Honduras","Guatemala"
)
# Retrievethe map data
some.la.maps <- map_data("world", region = some.la.countries)

# Compute the centroid as the mean longitude and lattitude
# Used as label coordinate for country's names
region.lab.data <- some.la.maps %>%
  group_by(region) %>%
  summarise(long = mean(long), lat = mean(lat))

ggplot(some.la.maps, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group, fill = region))+
  geom_text(aes(label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
  scale_fill_viridis_d()+
  theme_void()+
  theme(legend.position = "none")

```